### 2010-06-08 docs/architecture/architecture.tex
sync up with Makefile

The final lines in the {\tt GNUmakefile} include the rules to actually
build the executable.
\begin{verbatim}
  include $(FPARALLEL)/MAESTRO/GMaestro.mak
  include $(FPARALLEL)/mk/GMakerules.mak
\end{verbatim}

>>>>

The final line in the {\tt GNUmakefile} include the rules to actually
build the executable.
\begin{verbatim}
  include $(FPARALLEL)/MAESTRO/GMaestro.mak
\end{verbatim}
